---
title: "demographics"
output:
  pdf_document: default
  html_document: default
date: '2022-06-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(haven)
```


```{r}
german_df <- read_sav("../data/Compassion-DE_19 November 2023_19.42.sav")
```

```{r}
german_df
```

```{r}
filtered_german_df <- german_df %>% 
  filter(SOCS_O_10 == 4) %>% 
  filter(CEAS_TO1_4 == 10) %>% 
  filter(SCS_19 == 1) %>%
  filter(FFMQ_21 == 4)
```

```{r}
filtered_german_df %>% 
  write_csv("../results/german-complete-cases.csv")
```


```{r}
summarise_numerical <- function(df, column_name, demographic_name) {
  column_sym <- rlang::ensym(column_name)
  
  df %>%
    transmute(!!column_sym := as.numeric(!!column_sym)) %>% 
    filter(!is.na(!!column_sym)) %>% 
    summarise(mean = mean(!!column_sym), 
              std_dev = sd(!!column_sym), 
              min = min(!!column_sym), 
              max = max(!!column_sym), 
              N = n()) %>% 
    mutate(
      mean = round(mean, 2),
      std_dev = round(std_dev, 2),
      name=demographic_name
    )
}
```

```{r}
numerical_demo_df <- bind_rows(
  summarise_numerical(filtered_german_df, "DEM3", "Age"),
  summarise_numerical(filtered_german_df, "DEM1", "Number of Languages")
)
  
numerical_demo_df
```

```{r}
summarise_categorical <- function(df, column_name, recode_vector, demo_name) {
  column_sym <- rlang::ensym(column_name)
  demo_sym <- rlang::ensym(demo_name)

  summary_df <- df %>%
    mutate(!!demo_sym := as_factor(!!column_sym, ordered=TRUE)) %>%
    mutate(Category := fct_recode(!!demo_sym, !!!recode_vector)) %>% 
    filter(!is.na(Category)) %>% 
    count(Category) %>% 
    mutate(prop = round(n/sum(n) * 100, 2))
  
  total_df <- summary_df %>% 
    summarise(n := sum(n)) %>% 
    mutate(Category := demo_name)
  
  bind_rows(
    total_df,
    summary_df
  ) %>% 
    select(Category, n, prop)
}

```

```{r}
gender_recode <- c(Male="Mann",
      Woman="Frau",
      Other="von mir präferierte Bezeichnung",
      Other="bevorzuge nicht zu antworten"
    )
```

# Need translated Ethnicity

# Make sure these translations are double-checked

```{r}
education_recode <- c(
  "Left school without a secondary school qualification" = "Ich bin von der Schule abgegangen ohne Haupt-/Volksschulabschluss",
  "completed basic 6/8 years of education" = "Ich habe den Haupt-/Volksschulabschluss (oder frühere 8-klassige Schule)",
  "secondary school leaving certificate (11th grade, West Germany)" = "Ich habe Mittlere Reife/ Realschulabschluss",
  "polytechnic high school certificate (10th grade; East Germany)" = "Ich habe den Abschluss der Polytechnischen Oberschule 10. Klasse",
  "3 years technical college" = "Ich habe den Fachschulabschluss (ohne Anerkennung als Fachhochschulabschluss)",
  "general university entrance certificate" = "Ich habe die allgemeine oder fachgebundene Hochschulreife/Abitur (Gymnasium bzw. EOS) ohne abgeschlossenes Hochschul-/ Universitäts-studium",
  "college (≥ 4 years) or university degree" = "Ich habe ein abgeschlossenes Universitäts-/ Hochschul- bzw. Fachhochschulstudium (bzw. Fachschulabschluss mit Anerkennung als Fachhochschulabschluss)",
  "Other" = "Ich habe einen anderen Schulabschluss, und zwar:"
)
```

# Sexual Orientation (note: participants could select multiple)

```{r}
summarise_multi_select <- function(df, recode_df, regex_match, demo_name) {
  summary_df <- df %>% 
    select(matches(regex_match), ResponseId) %>% 
    mutate(across(-ResponseId, ~as.numeric(.x))) %>% 
    pivot_longer(-ResponseId, values_drop_na = TRUE) %>% 
    select(-value) %>% 
    mutate(value = as.numeric(str_split_i(name, '_', -1))) %>% 
    arrange(value) %>% 
    count(value) %>% 
    inner_join(recode_df, by = join_by(value==label_value)) %>% 
    select(Category = label, n) %>% 
    mutate(prop = round(n / sum(n) * 100, 2))

  summary_df %>%
    summarise(n = sum(n)) %>% 
    mutate(Category = demo_name) %>% 
    bind_rows(summary_df) %>% 
    select(Category, n, prop)
}
```

```{r}
orientation_recode <- c(`1` = "Heterosexual or straight", `2` = "homosexual, e.g., gay or lesbian", 
`3` = "bisexual", `4` = "fluid", `5` = "pansexual", `6` = "queer", 
`7` = "demisexual", `8` = "questioning", `9` = "asexual", `10` = "other [text entry]", 
`11` = "prefer not to respond")

orientation_recode_df <- data_frame(label=orientation_recode, label_value=as.numeric(names(orientation_recode)))
```


# Disability

```{r}
disability_recode <- c(
  "Yes" = "Ja",
  "No" = "Nein",
  "Prefer not to say" = "Ich würde lieber nicht antworten."
)

```

# Disability Type

(Mark all that apply): 1 = a sensory impairment (vision or hearing); 2 = a mobility impairment; 3 = a learning disability (e.g., ADHD, dyslexia); 4 = a disability or impairment not listed above

```{r}
disability_type_recode_df <- data_frame(
  label=c(
    "a sensory impairment (vision or hearing)",
    "a mobility impairment",
    "a learning disability (e.g., ADHD, dyslexia)",
    "a disability or impairment not listed above"
    ),
  label_value=1:4
)
```

# Mental Health Condition

```{r}
mental_condition_recode <- c(
  "Yes"= "Ja - bitte angeben (freiwillig)",
  "No" = "Nein",
  "Prefer not to specify" = "Ich würde lieber nicht anworten."
)
```

# Religion

Will need translation for Religion


# Parenting Status

```{r}
parenting_status_recode <- c(
  "No"="Nein",
  "No, but I am (or my partner is) pregnant or in the process of adopting"="Nein, aber ich (oder mein/e Partner/in) ist schwanger oder im Adoptionsprozess",
  "Yes"="Ja"
)
```

# Relationship Status


```{r}
marital_status_recode <- c(
  "Widowed" = "Verwitwet",
  "Married and living together" = "Verheiratet und zusammenlebend",
  "Single" = "Ledig",
  "Divorced" = "Geschieden",
  "Married but living separately" = "Verheiratet und getrennt lebend",
  "Other" = "Anderweitig (bitte angeben, wenn Sie möchten):",
  "Domestic partnership" = "Lebensgemeinschaft"
)
```

# All dfs

```{r}
numerical_demo_df <- bind_rows(
  summarise_numerical(filtered_german_df, "DEM3", "Age"),
  summarise_numerical(filtered_german_df, "DEM1", "Number of Languages")
)


categorical_demo_df <- bind_rows(
  summarise_categorical(filtered_german_df, "DEM4", gender_recode, "Gender"),
  summarise_multi_select(filtered_german_df, orientation_recode_df, "DEM5_\\d+$", "Sexual Orientation"),
  summarise_categorical(filtered_german_df, "DEM8", education_recode, "Education Level"),
  summarise_categorical(filtered_german_df, "DEM13_1", c(), "Subjective Perception of Socioeconomic Status"),
  summarise_categorical(filtered_german_df, "DEM15", disability_recode, "Disability"),
  summarise_multi_select(filtered_german_df, disability_type_recode_df, "DEM_16_\\d+$", "Disability Type"),
  summarise_categorical(filtered_german_df, "DEM14", mental_condition_recode, "Mental Health Condition"),
  summarise_categorical(filtered_german_df, "DEM12", parenting_status_recode, "Parenting Status Condition"),
  summarise_categorical(filtered_german_df, "DEM9", marital_status_recode, "Relationship Status")
)

```

```{r}
numerical_demo_df %>% 
  write_csv("../results/numerical_demo.csv")

categorical_demo_df %>% 
  write_csv("../results/categorical_demo.csv")
```


```{r}
sessionInfo()
```

